---
title: "Data Visualization"
author: "Agam Safaruddin"
---

::: callout-note
Most of my notes of studying this chapter is done in 'r-data-visualization.ipynb' (see workspace content). Just in case it is necessary to show it.
:::

# Requirements

## Libraries

Just simply get every library

```{r}
library(tidyverse)
library(readr)
library(ggplot2)
library(lubridate)
library(readxl)
library(knitr)
library(RSQLite)
library(data.table)
library(scales)
library(ggrepel)
```

## IMport data

```{r}
library(tidyverse)
covid_data_tbl <- read_csv("https://covid.ourworldindata.org/data/owid-covid-data.csv")
```

# Challenge 1

-   Goal: Map the time course of the cumulative Covid-19 cases

```{r}
covid_data_tbl %>% glimpse()
```

## Data Manipulation

```{r}
covid_data_dt = data.table(covid_data_tbl)
class(covid_data_dt)
#covid_data_dt
```

### Convert date to tb

```{r}
covid_data_dt[, date := as.Date(date)]
```

### extract year and month

```{r}
covid_data_dt[, year_month := format(date, "%Y-%m")]
```

### see result, and calculate total new cases for each month

```{r}
covid_data_new_cases_per_month_dt = covid_data_dt[!is.na(new_cases), .(new_cases_per_month = sum(new_cases)), by = .(year_month, location)]
covid_data_new_cases_per_month_dt
```

### filter locations

```{r}
chosen_locations = c("Germany", "United Kingdom", "France", "Spain", "United States")

covid_data_new_cases_per_month_per_chosen_locations_dt = covid_data_new_cases_per_month_dt[location %in% chosen_locations]

#covid_data_new_cases_per_month_per_chosen_locations_dt 
covid_data_new_cases_per_month_per_chosen_locations_dt %>% glimpse()
```

### cumulative calculation

```{r}
#covid_data_new_cases_per_month_per_chosen_locations_dt[, year_month := as.Date(year_month, format = "%Y-%m")]
covid_data_new_cases_per_month_per_chosen_locations_dt[, year_month := as.character(year_month)]
covid_data_new_cases_per_month_per_chosen_locations_dt[, cumulative_cases := cumsum(new_cases_per_month), by = .(location)]
```

### Get final cumulative number

```{r}
last_value = covid_data_new_cases_per_month_per_chosen_locations_dt %>%
  group_by(location) %>%
  filter(year_month == max(year_month)) %>%
  ungroup()
```

## Plot line graph

```{r}
ggplot(covid_data_new_cases_per_month_per_chosen_locations_dt, aes(x = year_month, y = cumulative_cases, color = location, group = location)) +
  geom_line() +

#geom_text(data = last_value, aes(label = cumulative_cases), hjust = 1, vjust = 1, color = "blue")+
geom_label_repel(data = last_value, aes(label = cumulative_cases), show.legend = TRUE, nudge_x = 0.01, nudge_y = 5000000, direction = "y") +
theme_dark() +
#theme_minimal() +
  #scale_x_date(date_labels = "%Y-%m", date_breaks = "1 month") +
theme(axis.text.x = element_text(angle = 45, hjust = 1, color = "black"),
        plot.title = element_text(face = "bold", color = "black"),
        plot.caption = element_text(face = "bold.italic", color = "black"),
        legend.position = "bottom",
     legend.text = element_text(color = "black"),
     legend.title = element_text(color = "black")) +
#theme_minimal() +

  labs(
    title = "Covid 19 confirm cases worldwdie",
    subtitle = "As of 19.04.2022",
    x = "Date",
    y = "Cumulative Cases",
    color = "Country"
      #show.legend = TRUE
  ) +
    scale_y_continuous(labels = function(x) paste0(x / 500000, "M")) 
                    

```
