---
title: "Test page"
author: "AgAm sAfaRuDdin"
---

::: callout-note
Notes go here ödnajkwdnöjanjlnald
:::

With eval: false

```{r}
#| eval: false
numbers <- 1:1000

# This will print the first 10 elements of the vector numbers
numbers[1:10]

# This will plot a histogram of 100 random elements of the vector numbers
hist(sample(numbers, 100, replace = T))
```

random calculate and print

```{r}
a=5
b=4
c=a+b
print(paste0(c))

```

with eval: true

```{r}
#| eval: true
numbers <- 1:1000

# This will print the first 10 elements of the vector numbers
numbers[1:10]

# This will plot a histogram of 100 random elements of the vector numbers
hist(sample(numbers, 100, replace = T))
```


* An (optional) YAML header surrounded by - - - at the top (there is no need in the beginning to alter it)
R code chunks surrounded by ```s. These chunks can be customized with knitr options, arguments set at the top of a chunk header after #|:
  + #| eval: false prevents running the code and include its results
  + #| include: false prevents code and results from appearing in the finished file. Quarto still runs the code in the chunk, and the results can be used by other chunks.
  + #| echo: false prevents code, but not the results from appearing in the finished file. This is a useful way to embed figures.
  + #| message: false prevents messages that are generated by code from appearing in the finished file.
  + #| warning: false prevents warnings that are generated by code from appearing in the finished.
  + #| fig-cap: "..." adds a caption to graphical results.

